\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-30 paper.tex
Polish the abstract

We identify the needed individual and collaborative cognitive
skills: geometric reasoning and situation assessment based on perspective-taking
and affordance analysis; acquisition and representation of knowledge models for
multiple agents (humans and robots, with their specificities); natural multi-modal dialogue;
human-aware task planning; human-robot joint task achievement. The article
discusses each of these abilities, presents a working implementation, and shows
how they combine in a coherent and original deliberative architecture for
human-robot interaction. Supported by experimental results, we eventually show
how explicit knowledge management, both symbolic and geometric, proves to be
instrumental to richer and more natural human-robot interactions by pushing for
pervasive, human-level semantics within the robot's deliberative system.

@@

The robot controller (with the help of a task planner) decides what action to
execute next, and who should perform it, from the robot or the human (or both in
case of a joint action). It finally controls and monitors its execution. The
operation continues until the goal is achieved, is declared unachievable or is
abandoned by the human~\cite{Klein2004}.

@@

We present first the main \emph{internal} cognitive capabilities, implemented in
the {\sc Oro} knowledge base itself, and then discuss successively the situation
assessment module {\sc Spark}, the dialogue processor {\sc Dialogs}, the
symbolic task planner HATP, and finally the main features of our execution
controllers {\sc Shary} and {\sc pyRobots}. Note that greater details on each of
these modules can be found in their respective publications (the corresponding
references are provided hereafter).

@@

{\sc Shary}'s originality, as an execution control system, lies in its ability
to take into account not only the task achievement but also the communication
and monitoring acts needed to support human-robot interactive task
achievement~\cite{Rich1997,Sidner2005} in a flexible manner. {\sc Shary} allows
to bind action execution to \emph{communication policies} in order to produce
signals towards the human and to react to human actions. The
\emph{communication act} is the central concept in this formalism. It
represents an information exchange between the two agents and plays the role of
a transition condition. This exchange can be realised through dialogue, by an
expressive motion or a combination of the two. It enables each agent to
communicate their beliefs about the task to be achieved, in order to share
mutual knowledge and to synchronise their activities.  This is done through
real-time task-based situation assessment achieved by the combination of {\sc
Shary} monitoring processes and {\sc Oro} inference
mechanisms~\cite{fiore2014}. \fixme{Rachid, reviewer 2 asks for more details
about this process -> M. Fiore work?}

@@

\subsubsection{Action Execution and Monitoring}\label{sec:action}

@@

The symbolic manipulation and navigation actions listed in
Table~\ref{table|pyrobots_actions} are eventually executed by the execution
controller with the help of a dedicated 3D motion planner (called {\sc Mhp},
Figure~\ref{fig|archi}): robot placement and end-effectors trajectories are
computed on-line to allow object manipulation that take into account task
specific constraints and human postures, abilities and preferences.  We kindly
refer the interested reader to~\cite{Sisbot2008, Mainprice2011, Pandey2011} for
details of these techniques.

>>>>

We identify the needed individual and collaborative cognitive skills: geometric
reasoning and situation assessment based on perspective-taking and
affordance analysis; acquisition and representation of knowledge models for
multiple agents (humans and robots, with their specificities); situated,
natural and multi-modal dialogue; human-aware task planning; human-robot
joint task achievement. The article discusses each of these abilities,
presents working implementations, and shows how they combine in a coherent
and original deliberative architecture for human-robot interaction.
Supported by experimental results, we eventually show how explicit knowledge
management, both symbolic and geometric, proves to be instrumental to richer
and more natural human-robot interactions by pushing for pervasive,
human-level semantics within the robot's deliberative system.

@@

The robot controller \cite{clodic2014key} (with the help of a task planner) decides what action to
execute next, and who should perform it, from the robot or the human (or both in
case of a collaborative action such as a handover \cite{Mainprice2012,waldhart2015planning}), how it should achieved and what signals should
be sensed and/or produced by the robot to facilitate human-robot joint action
\cite{sebanz2006joint,knoblich20113,pacherie2012phenomenology,vesper2010minimal}.
It finally controls and monitors its execution. The
operation continues until the goal is achieved, is declared unachievable or is
abandoned by the human~\cite{Klein2004}.

@@

We present first the main \emph{internal} cognitive capabilities, implemented in
the {\sc Oro} knowledge base itself, and then discuss successively the situation
assessment module {\sc Spark}, the dialogue processor {\sc Dialogs}, the
symbolic task planner HATP, and finally the main features of our execution
controllers {\sc Shary}\cite{clodic2008shary} and {\sc pyRobots}. Note that greater details on each of
these modules can be found in their respective publications (the corresponding
references are provided hereafter).

@@

{\sc Shary}'s originality, as an execution control system, lies in its ability
to take into account not only the task achievement but also the communication
and monitoring acts needed to support human-robot interactive task
achievement~\cite{Rich1997,Sidner2005,sebanz2006joint} in a flexible manner. {\sc Shary} allows
to bind action execution to \emph{communication policies} in order to produce
multi-modal signals towards the human and to react to human actions and signals. The
\emph{communication act} is the central concept in this formalism. It
represents an information exchange between the two agents and plays the role of
a transition condition. This exchange can be realised through speech, through an
expressive motion or a combination of the two. It enables each agent to
communicate their beliefs about the task to be achieved, in order to share
mutual knowledge and to synchronise their activities.  This is done through
real-time task-based situation assessment achieved by the combination of {\sc
Shary} monitoring processes and {\sc Oro} inference
mechanisms.

Two recent developments have been added that improve robot adaptation to human action at the action and at the plan level.  In~\cite{fiore2014}, the system is able to estimate its human intentions in collaborative tasks and to choose appropriate actions, using a set of POMDP models.  In~\cite{devin2016implemented}, a framework is proposed which allows the robot to estimate its human partner mental state not only about the environment but also about the state of goals, plans and actions and to take them into account when executing human-robot shared plans.

@@

\subsubsection{Action Refinement, Execution and Monitoring}\label{sec:action}

@@

The symbolic manipulation and navigation actions listed in
Table~\ref{table|pyrobots_actions} are eventually further refined and executed by the execution
controller with the help of a  set of dedicated human-aware geometric motion
planning functions provided by a component (called {\sc Mhp},
Figure~\ref{fig|archi}).

These functions are designed to plan navigation~\cite{Sisbot2007} and
manipulation~\cite{Mainprice2011,sisbot2012human} paths not only safe
but also comfortable and “socially acceptable” by reasoning explicitly
on human’s kinematics, vision field, posture and preferences
\cite{Madhava2006,kruse2013human,Rios-MartinezSL15}.  Besides, when necessary, they compute pertinent robot
and objects placements relative to the human\cite{Pandey2011}

Also, when an action needs motion of the human and the robot, it is
possible to plan for both of them in order to allow the robot to take
initiative by computing automatically where the interaction might
preferably take place\cite{Mainprice2012,waldhart2015planning}, 
thus decreasing the cognitive weight of interaction on human
side. This is somehow the geometric counterpart of HATP.
